\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{needspace}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagecolor{white}
\color{black}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \Needspace{5\baselineskip}
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://jonahseguin.com/}{\Large Jonah Seguin}} & Email: \href{mailto:me@jonahseguin.com}{me@jonahseguin.com}\\
  \href{https://jonahseguin.com/}{jonahseguin.com}\\
  Montréal, QC, Canada\\
\end{tabular*}

%
%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: JavaScript, TypeScript, Rust, Java, Kotlin, Python, SQL, HTML, CSS }
   }
   \item{
    \textbf{Technologies}{: Node, MongoDB, Redis, MySQL, PostgreSQL, Docker, Kubernetes, Puppeteer, AI SDK }
   }
   \item{
    \textbf{Frameworks}{: React, Next, Vue, Express, Hono, tRPC, Prisma, Drizzle, TanStack, Tailwind, shadcn/ui }
   }
    \item{
    \textbf{Platforms}{: GitHub, Vercel, Cloudflare, Stripe, Twilio, Railway, AWS, OpenAI, Anthropic, Convex }
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Internet Backyard, Inc.}{}
      {Founding Member of Technical Staff}{Dec 2025 - Present}
      \resumeItemListStart
        \item
          {Building the Financial Backbone for Compute.}
      \resumeItemListEnd

    \resumeSubheading
      {Zero Email, Inc. (Mail0, YC X25)}{}
      {Lead Founding Software Engineer}{Aug 2025 - Dec 2025}
      \resumeItemListStart
        \item
          {Designed and implemented core backend infrastructure using TypeScript, Convex, and Cloudflare Workers, with a focus on reliability, scalability, and developer velocity.}
        \item
          {Built the Next.js frontend and engineered data synchronization with major email providers; delivered AI-driven email processing and platform integrations to enable workflow automations.}
      \resumeItemListEnd

    \resumeSubheading
      {TryClover, Inc. (Clover Labs)}{}
      {Senior Software Engineer}{May 2025 - Aug 2025}
      \resumeItemListStart
        \item
          {Built a TypeScript/Bun + Supabase backend for an AI agent that monitors social keywords, generates/schedules posts and comments, and sends Slack alerts (OpenAI, Puppeteer/Browserbase).}
        \item
          {Shipped browser automation and scraping, database design, and a Next.js/React UI from Figma (Tailwind CSS); drove code reviews, prompt tuning, performance, and tech-debt reduction.}
      \resumeItemListEnd

    \resumeSubheading
      {Fuzey Designs, LLC.}{}
      {Senior Software Engineer}{Nov 2024 - Aug 2025}
      \resumeItemListStart
        \item
          {Reduced infrastructure costs by 84\% through optimized microservice architecture, caching, code efficiency, and request de-duplication, improving scalability and performance.}
        \item 
          {Enhanced user experience by optimizing media streaming and encoding, resulting in faster page load times and smoother playback.}
        \item
          {Improved security and reliability by transitioning database and services to a private network and automating daily database backups.}
        \item
          {Boosted application functionality by implementing programmatic media capture, advanced analytics, and secure email/SMS authentication, enhancing user engagement and insights.}
      \resumeItemListEnd

    \resumeSubheading
      {Akuma Games, LLC.}{}
      {Senior Software Engineer}{Jan 2022 - Nov 2024}
      \resumeItemListStart
        \item
          {Architected and implemented a full-stack web application featuring real-time chat, social media-style posts, rich player statistics, account linking, and a digital/fiat currency storefront.}
        \item 
          {Developed and deployed an automated multi-environment DevOps pipeline for microservices, utilizing Kubernetes clusters for seamless environment-specific deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {Hypixel, Inc.}{}
      {Software Engineer}{Nov 2020 - Nov 2021}
      \resumeItemListStart
        \item
          {Led a security project to address server code vulnerabilities, resulting in a 90\% reduction in security incidents.}
        \item
          {Collaborated with a team of 30 engineers to develop, test, and release over 50 weekly updates for games, supporting over 200,000 concurrent users.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Universal Music Group}{}
      {Software Engineer, Research \& Development}{Aug 2020 - Nov 2020}
      \resumeItemListStart
        \item
          {Assisted in building and testing a full-stack web application for content creators to purchase licenses for UMG music in videos.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Hylist Games, LLC.}{}
      {Software Engineer}{Oct 2019 - Aug 2020}
      \resumeItemListStart
        \item
          {Managed and rolled out 50+ updates to production game servers, serving over 1 million unique users.}
        \item
          {Employed Agile methodologies to deliver features in weekly sprints, participating in meetings, daily stand-ups, and pair programming sessions.}
        \item
          {Migrated the codebase to Continuous Integration and Continuous Deployment (CI/CD) pipelines, reducing onboarding time by up to one hour and enhancing developer experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://sock8.com}{sock8}}
      {WebSockets-as-a-service API and SDK for real-time full-stack Next.js applications with end-to-end type safety.}
    \resumeSubItem{\href{https://overlayz.io}{overlayz.io}}
      {Web-based interactive editor for creating overlays for streaming and recording with real-time data.}
    \resumeSubItem{\href{https://github.com/tsanga/orbt}{orbt}}
      {Real-time web application with an embedded multiplayer browser for collaborative media consumption.}
    \resumeSubItem{\href{https://github.com/tsanga/musty}{musty}}
      {Open source database-agnostic NoSQL object-document wrapper library for Rust applications.}
    \resumeSubItem{\href{https://github.com/jonahseguin/drink}{drink}}
      {Open source dependency-injection command and argument parsing library for Java applications.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
